\documentclass{article}

\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{ltablex}
\usepackage[paper=portrait,pagesize]{typearea}

\hypersetup{
    colorlinks=true,       % false: boxed links; true: colored links
    linkcolor=red,          % color of internal links (change box color with linkbordercolor)
    citecolor=green,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=cyan           % color of external links
}

\title{Hazard Analysis\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle
\thispagestyle{empty}

~\newpage

\pagenumbering{roman}

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
Date1 & Name(s) & Description of changes\\
Date2 & Name(s) & Description of changes\\
... & ... & ...\\
\bottomrule
\end{tabularx}
\end{table}

~\newpage

\tableofcontents

~\newpage

\pagenumbering{arabic}

% \wss{You are free to modify this template.}

\section{Introduction}

% \wss{You can include your definition of what a hazard is here.}

Analyzing the hazards associated with a system is an important step in
developing a safe and reliable product. It helps identify and evaluate
potential risks that could impact the safety or usability of the system. By
conducting a hazard analysis before development, we can take proactive measures
to mitigate these risks, and design preventative measures to ensure the system
operates as intended.
\\
\\
For our note-taking system (\progname), this analysis focuses on hazards that 
may lead to data loss, perfomance issues, and security vulnerabilities. As 
\progname aims to procide fast keyword-based editing with real-time diagram
rendering, it introduces potential risks in different areas including rendering
performance, data integrity, and user experience.
\\
\\
The following sections of the document define the scope and objectives of the 
hazard analysis, describe the system boundaries and main components of 
\progname, and outline key assumptions that may influence saftey considerations.
The core of the document presents a detailed Failure Mode and Effect Analysis
(FMEA) table, which identifies potential hazards, their causes and effects.
Finally, the document concludes with a summary of safety and security
requirements, and provides a roadmap for implementing these requirements in
future development phases.

\section{Scope and Purpose of Hazard Analysis}

% \wss{You should say what \textbf{loss} could be incurred because of the hazards.}
The purpose of this hazard analysis is to identify and evaluate the potential 
risks that could impact the safety, security, and usability of \progname. 
Conducting this analysis in the early stages of development allows for us to 
anticipate possible failure points in the system and implement design strategies
to prevent data loss, ensure stable performance, and maintain user confidence.
\\
\\
The text-editing interface, diagram rendering engine, and file storage system all 
make up the core components of \progname. This analysis will focus on both 
software related hazards, such as crashes, performance issues, and 
synchronization errors, as well as user-related risks, including data loss, 
security vulnerabilities, and unintuitive user interactions.
\\
\\
Losses that may be incurred due as a result of these hazards include:
\begin{itemize}
    \item \textbf{Loss of user data} from failed saves, corruption, or unexpected
    application closures
    \item \textbf{Loss of productivity} due to lag, unresponsiveness or
    unintuitive interface or command design
    \item \textbf{Loss of reliability and maintainability} if the application 
    is developed with technical dept or poor coding practices
    \item \textbf{Loss of user trust} due to repeated bugs, confusing features,
    or inconsistent behavior
    \item \textbf{Loss of security or privacy} if data is not properly protected
    or stored securely
\end{itemize}

The hazard analysis focuses on factors in the software domain only. While
hardware failures (e.g., device crashes, power loss), as well as operating
system issues (e.g., file system corruption, OS crashes) can impact the
performance and reliability of \progname, these are outside the scope of this
analysis. \progname will be running in the user space and any potential
problems occuring at the kernal level or below are will therefore not be 
considered. The analysis will assume that the underlying hardware and OS
are functioning correctly, and will focus on hazards that can be directly
attributed to the design and implementation of \progname itself.


\section{System Boundaries and Components}

% \wss{Dividing the system into components will help you brainstorm the hazards.
% You shouldn't do a full design of the components, just get a feel for the major
% ones.  For projects that involve hardware, the components will typically include
% each individual piece of hardware.  If your software will have a database, or an
% important library, these are also potential components.}
\progname is a note-taking application that allows users to create, edit, and
visualize text-based diagrams using only keyboard inputs. The boundaries of
the system include all components directly related to the core functionality of
the application, including taking user input, rendering diagrams, and file 
management. The system boundary does not include external dependencies such as 
the user's operating system, device hardware, or third-party file storage services 
such as cloud storage providers.
\\
\\
The main components of \progname include:
\begin{enumerate}
    \item \textbf{User Interface (UI) Layer}
    \begin{itemize}
        \item Handling user interactions, keyboard inputs, displaying updates
        \item Showing live view of notes and diagrams
        \item Providing feedback on actions (e.g., error messages)
    \end{itemize}
    \item \textbf{Command Processing Engine}
    \begin{itemize}
        \item Parsing and interpreting user commands
        \item Managing application state based on user inputs
        \item Sending structured actions to the rendering and storage layers
    \end{itemize}
    \item \textbf{Diagram Rendering Engine}
    \begin{itemize}
        \item Converting text-based diagram descriptions into visual formats
        \item Handling shape layout, positioning, and connection to the rest of
        the note content
    \end{itemize}
    \item \textbf{File Management and Storage Layer}
    \begin{itemize}
        \item Saving and loading notes and diagrams to/from disk
        \item Managing file formats and data serialization
        \item Ensuring data integrity during read/write operations
    \end{itemize}\
    \item \textbf{Error Handling and State Management Module}
    \begin{itemize}
        \item Detecting, logging, and managing errors across all components
        \item Implementing recovery mechanisms and stability after crashes or
        unexpected shutdowns
    \end{itemize}
    % \item \textbf{Configuration/Customization Module} %potential future 
    % component
    % \begin{itemize}
    %     \item Storing and Managing user preferences and application settings
    % \end{itemize}
\end{enumerate}

In addition to these core components, \progname may also depend on external
libraries for specific functionalities, such as diagram rendering or parsing.
To generate and display diagrams, the application may utilize a graphics 
library to allow for efficient rendering and manipulation of visual elements.
For parsing user commands, a parsing library may be employed to simplify the
interpretation of complex inputs. State management libraries may also be used
to help maintain application state and ensure consistency across different
components.


\section{Critical Assumptions}

% \wss{These assumptions that are made about the software or system.  You should
% minimize the number of assumptions that remove potential hazards.  For instance,
% you could assume a part will never fail, but it is generally better to include
% this potential failure mode.}
Certain key assumptions will be made regarding the user and operating environment
during the development and use of \progname. These assumptions include:
\\
\\
\begin{enumerate}
    \item \textbf{User Competency:} It is assumed that users have a basic level
    of computer literacy and is familiar with computer opertations such as using
    a keyboard and mouse. Users are expected to follow reasonable usage patterns
    (e.g. not shutting down the application abruptly or attempting to
    manipulate internal files directly).
    \item \textbf{File Access and Storage:} It is assumed that the file system
    used for storing notes and diagrams is reliable and free from corruption.
    Users are expected to have sufficient permissions to read/write files in
    the designated storage locations.
    \item \textbf{Operating Environment:} It is assumed that \progname will be
    run on a supported operating system without unexpected interruptions such
    as forced shutdowns, crashes, or power failures. The system is expected to
    have adequate disk space and memory to run the application smoothly.
    \item \textbf{Software Dependencies:} It is assumed that any third-party
    libraries or frameworks used by \progname are stable, compatible, and
    function as intended on the target operating systems. 
\end{enumerate}

% Make new landscape page for FMEA table
\newpage
\KOMAoptions{paper=landscape,DIV=12,pagesize}
\recalctypearea

\section{Failure Mode and Effect Analysis}

% \wss{Include your FMEA table here. This is the most important part of this 
% document.}
% \wss{The safety requirements in the table do not have to have the prefix SR.
% The most important thing is to show traceability to your SRS. You might trace 
% to requirements you have already written, or you might need to add new
% requirements.}
% \wss{If no safety requirement can be devised, other mitigation strategies can 
% be entered in the table, including strategies involving providing additional
% documentation, and/or test cases.}
\small
\newcolumntype{A}{>{\hsize=.5\hsize}X}
\newcolumntype{B}{>{\hsize=.8\hsize}X}
\newcolumntype{C}{>{\hsize=1.4\hsize}X}
\newcolumntype{D}{>{\hsize=.7\hsize}X}
\begin{tabularx}{\textwidth}{A B B B B C A}
\caption{Failure Mode and Effect Analysis (FMEA) for \progname}  \\
\toprule
\textbf{Design Function} & \textbf{Failure Modes} & \textbf{Effect of failure} &
 \textbf{Causes for failure} & \textbf{Detection} & \textbf{Recommended actions} 
 & \textbf{SR}\\
\midrule

\endfirsthead
\caption{Failure Mode and Effect Analysis (FMEA) for \progname}  \\
\toprule
\textbf{Design Function} & \textbf{Failure Modes} & \textbf{Effect of failure} &
 \textbf{Causes for failure} & \textbf{Detection} & \textbf{Recommended actions} 
 & \textbf{SR}\\
\midrule
\endhead

Diagram rendering and layout & Overlapping shapes, unreadable layout, slow 
rendering & Reduced usability, user spending more time rearranging rather 
than note taking & Poor algorithm layout, too large graphics & Creation shows
long frame times, UI freezes, user complaints, perfomance test threshold time 
limit exceeded & Have Unit tests performance tests for frame time; Use worker 
threads for rendering; Set rendering performance limits (e.g. <100ms per 
update); Implement partial rendering (e.g. rendering visual portion first); 
Potentially user to pin diagram positions & (F232, NF231) \\ \midrule
Command parsing & Parser misinterprets or fails to parse user input & 
Unexpected or no diagram output, lost note, user confusion/frustration & 
Unintuitive grammar, improper user input, unhandled exceptions & Parser 
exception and logs, failed rendering, regression tests failing on inputs & 
Define simple, well-documented grammar and implement intuitive parser with
proper error message handling; Provide immediate syntax validation (e.g. 
highlight errors); Fuzz unit tests to handle any and all errors; On parse 
error, preserve raw text and do not delete it & (F221, NF221) \\ \midrule
Load/Open note & Note fails to load, note partially loads, note produces 
wrong rendering & User cannot access previous work, user confusion/frustration,
loss of user trust & Incompatible or invalid file format, deserialization 
error & Load exceptions, visual regression tests, user reports & File format 
version tag with schema validation during load; Save raw text of error log,
tests for loading after saving & (F241, F243, F244, NF241) \\ \midrule
Save note & File not saved, save interrupted & File missing or corrupted, 
Loss of notes or diagrams, decrease in user productivity, loss of user trust 
in application & Power loss mid-save, app crash during write, full file 
storage & Exceptions logged, file hash value (or checksum) mismatch, 
unexpected file size, user reported missing file & Implement autosaving or 
atomic saving (save to temp file and rename it); Verify with checksumes on 
save and load; Inform user of insufficient disk space before save; Unit 
tests for save routines & (F241, F243, F244, NF241) \\ \midrule
Keybinding Commands & Key conflicts, lost keystrokes (commands done
unexpectedly) & Inability to create note, user frustration, potential data
loss from unintended commands done (e.g. Alt+F4) & Global shortcut 
overlapping (e.g. Ctrl+C natively means copy), race conditions in input 
handling & Unit tests for commands, integration tests under different 
environments, user reports & Allow for remappable keybinding (with safe
default set); Expose preview of keybinds; Provide undo command / option &
(F222, NF223) \\ \midrule
Interacting with shapes or diagrams (Add Text, Move, etc) & Edit commands 
behave incorrectly, loss of shape selection, text addition is 
inconsistent/undesired & Wrong edits made, user frustration, 
possible data corruption if partial edits made or deletes of inccorect item & 
Text and visual model not in sync, race conditions in input handling, 
undo stack not properly managed & Unit tests for edit commands and sequences
of commands, user reports & Implement robust undo/redo stack; Integration 
testing simulating keyboard macros; Sync checks for text and visual model;
Provide visual feedback on selection and edits; & (F216, NF212) \\ 
\midrule
Custom Geometry creation (user-defined shapes) & Custom shapes fail to render, 
Shapes cannot be reusedd reliably & User time wasted recreating shapes, loss of
user trust in customization features & Improper serialization or 
deserialization, ambiguous grammar for custom shapes, render limitations & 
Save or load of custom shapes fails, unit tests for custom shape rendering and 
serialization, user reports & Define clear grammar for custom shapes; Test 
creating, saving, loading, and rendering custom shapes; Initially limit 
complexity of custom shapes (e.g. no nested shapes); & (F215) \\
\midrule
Save custom geometry as reusable commands & Command fails to save, Command 
working incorrectly & Loss of user productivity, Command produces wrong output, 
parse crashes, user frustration & Poor macro serialization, syntax collisions, 
improper parsing & Macro creation errors logged, regression tests for macros, 
user reports & Isolate macros syntax from normal command syntax; Provide clear
error messages on macro creation; Unit tests for macro creation, saving, 
loading, and execution; & (F251) \\ \midrule
Overall performance / responsiveness vs alternatives & Easier and more 
intuitive to take notes on other apps, app feels slower than existing tools 
(e.g. laggy rendering) & Users revert to other tools, poor adoption of app & 
Inefficient algorithms, full rendering on every change, blocking main thread & 
User performance testing, user feedback, collecting performance metrics & 
Incrementally render (diagram first, then text); If document becomes large, 
only render visible portion; Use worker threads for rendering; Performance 
budgets for each operation (e.g. <100ms for rendering update); Measure 
against alternative apps in user tests & (NF 211, NF212) \\
\bottomrule
\end{tabularx}

% Revert back to portrait for the rest of the document
\newpage
\KOMAoptions{paper=portrait,DIV=8,pagesize}
\recalctypearea

\section{Safety and Security Requirements}

\wss{Newly discovered requirements.  These should also be added to the SRS.  (A
rationale design process how and why to fake it.)}

\section{Roadmap}

\wss{Which safety requirements will be implemented as part of the capstone timeline?
Which requirements will be implemented in the future?}

\newpage{}

\section*{Appendix --- Reflection}

\wss{Not required for CAS 741}

\input{../Reflection.tex}

\begin{enumerate}
    \item What went well while writing this deliverable? 
    \begin{itemize}
        \item Chengze - I found that our team collaborated effectively in dividing the work 
        and keeping our analysis consistent across sections. We communicated clearly about 
        potential hazards and quickly agreed on the scope and structure of the document. 
        Using LaTeX templates also helped maintain a clean and professional format throughout.
        \item Ethan - I think something that went well in this deliverable was
          the team collaboration. Everyone communicated well and we tried our
          best to have PRs up and a proper review process. We learned from our
          last deliverable that saving review to the last minute makes it
          really hard to actually incorporate the feedback, but it was better
          in this milestone.
        \item Hussain - Being assigned to work on the first 5 sections of this document
        went well. I think this was because these sections were more straightforward
        and easier to write. I was able to also have a good understanding of the
        project, which made it easier to write these sections.
        \item Jeffrey - Regarding the Hazard Analysis document, I found that
        coming up with safety requirements went very well. The team had discussed
        in passing possible features and safety concerns prior to this deliverable.
        From those discussions, we were able to recall and document those in the
        Hazard Analysis document. Additionally, I found that further discussion on
        what new safety requirements should be added in section 6 of this document
        went smoothly. The team was able to discuss new points after taking a break
        and coming back to the section as a whole team.
        \item Kevin - Kevin - Our group managed to smoothly assign work and a work 
        to review to each member. This was done in group meetings and was helpful 
        as it meant we could fit the work to our schedules, meaning that we did not 
        have to find times we could meet to do work. These times were reserved for 
        asking each other questions and making sure our work lined up with each 
        others. Note that I did not work on the HA document and this is related to 
        my work on the SRS instead.
    \end{itemize} 
    \item What pain points did you experience during this deliverable, and how
    did you resolve them?
    \begin{itemize}
        \item Chengze - A main difficulty was completing some parts of the hazard analysis 
        without direct communication among team members, since it is closely related to the 
        SRS content. Some sections depended on finalized requirements or component details 
        that were still being developed. We resolved this by holding short sync meetings and 
        clarifying assumptions so our analysis stayed consistent with the SRS.
        \item Ethan - It was difficult to think about hazards related to our
          product, since our project is purely software and doesn't really have
          any potential physical harm to users or the environment. We resolved
          this by working as a team and brainstorming other hazard areas that
          we wouldn't typically think of at first.
        \item Hussain - Section 5 (FMEA) was a pain point for me. I think this was
        because it was the most technical section, and it required a lot of
        thinking and analysis. It also related to other parts of this and the SRS
        document, which made it harder to write. To resolve this, I reviewed my 
        teammates' sections to get a better understanding of the project, and I also
        asked my teammates for help when I was struggling with certain parts.
        \item Jeffrey - During this deliverable, I expereinced issues / pain points
        with trying to link back between the SRS and this Hazard Analysis document. 
        The main concern was that portions of this document relied on the SRS which
        was not fully completed at the time of working on the Hazard Analysis.
        In order to resolve this, I decided to communicate with the member who was
        working on that portion of the SRS and asked them to share their ideas/thoughts
        with me prior to them pushing and merging onto the GitHub so I can work on may
        section simultaniously. This allowed both sections to be completed in a timely
        manner. If we made changes or had questions about each others portion, we 
        quickly notified the other individual to make the changes accordingly.
        \item Kevin - One pain point of this deliverable was the large volume of work. 
        As this SRS was a project that took us the whole semester to finish last year. 
        However, as we are now more experienced and understand better how to write the 
        SRS it took less time as we knew what to write without second guessing 
        ourselves.
    \end{itemize} 
    \item Which of your listed risks had your team thought of before this
    deliverable, and which did you think of while doing this deliverable? For
    the latter ones (ones you thought of while doing the Hazard Analysis), how
    did they come about?
    \begin{itemize}
        \item Our team had already identified general risks such as 
        data loss and performance issues early in the SRS phase. However, while 
        doing this deliverable, we recognized new risks related to user input 
        handling and rendering consistency in the canvas editor. These came up 
        as we analyzed possible failure modes and realized how improper error 
        handling or unexpected user actions could lead to crashes or corrupted note files. 
    \end{itemize} 
    \item Other than the risk of physical harm (some projects may not have any
    appreciable risks of this form), list at least 2 other types of risk in
    software products. Why are they important to consider?
    \begin{itemize}
        \item Some important types of risk in software products are data security 
        risks and usability risks. Data security risks, such as unauthorized access or data 
        corruption, can lead to loss of user trust and legal issues. Usability risks, like 
        confusing interfaces or unclear workflows, can reduce user satisfaction and prevent 
        adoption of the software. Considering these risks early helps ensure both system 
        reliability and a positive user experience. Another risk may be financial risk, 
        where project delays or cost overruns could impact the viability of the product.
        If the project runs out of budget or takes too long to deliver, it may not be
        feasible to continue development or support.
    \end{itemize} 
\end{enumerate}

\end{document}
