\documentclass{article}

\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{ltablex}
\keepXColumns
\usepackage{float}

\title{Reflection and Traceability Report on \progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

\plt{Reflection is an important component of getting the full benefits from a
learning experience.  Besides the intrinsic benefits of reflection, this
document will be used to help the TAs grade how well your team responded to
feedback.  Therefore, traceability between Revision 0 and Revision 1 is and
important part of the reflection exercise.  In addition, several CEAB (Canadian
Engineering Accreditation Board) Learning Outcomes (LOs) will be assessed based
on your reflections.}

\section{Changes in Response to Feedback}

\plt{Summarize the changes made over the course of the project in response to
feedback from TAs, the instructor, teammates, other teams, the project
supervisor (if present), and from user testers.}

\plt{For those teams with an external supervisor, please highlight how the feedback
from the supervisor shaped your project.  In particular, you should highlight the
supervisor's response to your Rev 0 demonstration to them.}

\plt{Version control can make the summary relatively easy, if you used issues
and meaningful commits.  If you feedback is in an issue, and you responded in
the issue tracker, you can point to the issue as part of explaining your
changes.  If addressing the issue required changes to code or documentation, you
can point to the specific commit that made the changes.  Although the links are
helpful for the details, you should include a label for each item of feedback so
that the reader has an idea of what each item is about without the need to click
on everything to find out.}

\plt{If you were not organized with your commits, traceability between feedback
and commits will not be feasible to capture after the fact.  You will instead
need to spend time writing down a summary of the changes made in response to
each item of feedback.}

\plt{You should address EVERY item of feedback.  A table or itemized list is
recommended.  You should record every item of feedback, along with the source of
that feedback and the change you made in response to that feedback.  The
response can be a change to your documentation, code, or development process.
The response can also be the reason why no changes were made in response to the
feedback.  To make this information manageable, you will record the feedback and
response separately for each deliverable in the sections that follow.}

\plt{If the feedback is general or incomplete, the TA (or instructor) will not
be able to grade your response to feedback.  In that case your grade on this
document, and likely the Revision 1 versions of the other documents will be
low.}

\subsection{SRS and Hazard Analysis}

\begin{tabularx}{\textwidth}{>{\hsize=0.4\hsize}X >{\hsize=0.8\hsize}X >{\hsize=1.8\hsize}X}
\toprule
\textbf{Source} & \textbf{Feedback Summary} & \textbf{Response / Change Made} \\
\midrule
\endfirsthead
\toprule
\textbf{Source} & \textbf{Feedback Summary} & \textbf{Response / Change Made} \\
\midrule
\endhead
\bottomrule
\endfoot
Team 19 (peer review) &
  HA Section 3 excluded cloud storage from the system boundary, but the Roadmap referenced cloud save as a deferred feature, creating an inconsistency. &
  Updated HA Section 3 to state that cloud storage and multi-user access are planned future features outside the current capstone scope. Updated HA Section 7 (Roadmap) to consistently name ACR1 and UR2 as the deferred requirements and to remove the ambiguous ``cloud save is not part of our capstone timeline'' phrasing. \\
\midrule
Team 19 (peer review) &
  FMEA table contained no security-related failure modes, despite Section~6 including UR1 (restricting malicious file uploads) and ACR1 (unauthorized access). This left a gap between the identified security requirements and the hazard analysis. &
  Added a new FMEA row ``File import / upload'' covering the failure mode of the application accepting a restricted or malicious file type (.exe, .js, .bat, .sh). Includes causes, detection methods, and recommended mitigations (allowlist validation, rejection with error message, test coverage). References (F243); \S6: UR1. ACR1 is already deferred (cloud phase) and addressed by the note added in the earlier fix. \\
\midrule
Team 23 (peer review) &
  Assumption~1 (User Competency, §4) stated users are expected ``not shutting down the application abruptly,'' effectively hand-waving away a predictable user action. Software must be resilient to abrupt termination regardless of user intent. &
  Removed ``not shutting down abruptly'' from Assumption~1; replaced with an explicit statement that abrupt termination is a predictable action the system must tolerate. Updated the ``Save note'' FMEA mitigation to state autosave and atomic saving are core required features (not optional), and added crash-recovery on next launch and simulated-termination unit tests. \\
\midrule
Team 23 (peer review) &
  Roadmap only stated all requirements would be implemented during the capstone timeline, with no milestones or references to when/where each mitigation would be validated. &
  Added a paragraph to the Roadmap linking mitigations to project phases: high-risk items (save, load, file import) targeted for Rev~0; medium-risk items (rendering, parsing, keybindings, shape editing) addressed across Rev~0 and verified in VnV; lower-risk items (custom geometry, macros) targeted for Rev~1. All mitigations confirmed through VnV prior to final demo. \\
\midrule
Team 23 (peer review) &
  FMEA table lacked risk ranking (severity, likelihood, detectability), making it impossible to prioritize which hazards must be addressed first. &
  Added a Risk Level column (High / Medium / Low) to the FMEA table based on combined severity and likelihood. Added a legend above the table defining the rating criteria. Ratings assigned: Save note and Load/Open note --- High; File import/upload --- High; Diagram rendering, Command parsing, Keybinding Commands, Shape interaction, Overall performance --- Medium; Custom Geometry creation and Save custom geometry --- Low. \\
\midrule
Team 23 (peer review) &
  Claimed many FMEA mitigations are reactive rather than preventive. The broad claim is overstated---most rows already contain preventive strategies (atomic saves, schema validation, worker threads, grammar isolation). However, the specific ``Load/Open note'' mitigation ``Save raw text of error log'' was purely reactive detection and not a true mitigation. &
  Replaced ``Save raw text of error log'' in the ``Load/Open note'' row with: preserve the original file without modification on validation failure; maintain a backup copy of the last known-good save for rollback. The remaining mitigations across other rows were left unchanged as they are already predominantly preventive or corrective. \\
\midrule
Team 19 (peer review) &
  Critical Assumption~3 (§4) stated \progname\ runs ``without unexpected interruptions such as forced shutdowns, crashes, or power failures,'' but the FMEA ``Save note'' row explicitly treats power loss mid-save as a real hazard with mitigations. This created a direct contradiction. &
  Updated Assumption~3 to scope OS stability to kernel/driver-level correctness only, and explicitly noted that power failures and forced shutdowns are \emph{not} assumed away---pointing to the FMEA's atomic-save and checksum mitigations as the intended response. \\
\midrule
Team 19 (peer review) &
  ACR1 in Section 6.1 (``Users will not be able to access documents and notes written by other users'') conflicts with Section 3, which places cloud storage outside the system boundary. ACR1 implies a multi-user/cloud context but appeared as an active requirement with no qualification. &
  Added a note to ACR1 clarifying it is deferred to the planned cloud save phase and does not apply to the current local-only system. Added a \texttt{\textbackslash label} to the Roadmap section and cross-referenced it from the note. (Related to Issue~1 fix, which updated Sections~3 and~7 but left Section~6.1 unresolved.) \\
\midrule
Team 19 (peer review) &
  F243 (Export/Import to PDF/Markdown) was incorrectly cited in the ``Load/Open note'' and ``Save note'' FMEA rows; those mitigations address data integrity and file system reliability, not export/import compatibility. &
  Removed F243 from both the ``Load/Open note'' and ``Save note'' Req.\ Refs entries. Remaining references (F241, F244, NF241) correctly cover file operations, version history/rollback, and the data integrity non-functional requirement. \\
\midrule
Team 19 (peer review) &
  FMEA table SR column only referenced SRS requirement IDs (F/NF codes); no link to the Section 6 Safety and Security Requirements (ACR1, SR1, IR1, CR1, CR2, etc.), making traceability difficult. &
  Renamed the FMEA column header from ``SR'' to ``Req.\ Refs'' and appended the relevant Section 6 safety/security requirement IDs (prefixed ``\S6:'') to each row. Mapping: Diagram rendering~--- CR1; Command parsing~--- IR1, CR2; Load/Open note~--- SR1, IR1, CR2; Save note~--- SR1, IR1; Keybinding Commands~--- IR1; Shape interaction~--- IR1; Custom Geometry~--- IR1, CR1; Custom commands~--- IR1, CR2; Overall performance~--- CR1. \\
\midrule
Team 19 (peer review, SRS) &
  S.7 security requirements were a bare list with no attack scenarios, handling strategies, or boundary conditions, making the coverage difficult to evaluate. &
  Rewrote S.7 based on actual implementation: added threat model intro; annotated each requirement with Threat and Handling based on verified code behaviour (no outbound network confirmed in main/index.ts; OS dialog extension filter for UR1; console-only stack traces for CR2). Honestly noted current limitations: no magic-byte checking (UR1), atomic writes not yet implemented (IR1), no CI dependency audit (CR1). \\
\midrule
Team 19 (peer review, SRS) &
  S.6 acceptance criteria used vague language (``responds within acceptable delay,'' ``runs smoothly'') with no measurable thresholds, making formal verification impractical. &
  Rewrote the S.6 acceptance criteria table with concrete, testable thresholds referencing existing NF requirements: 50ms canvas response (NF212), 30ms command execution (NF221), 60fps on 100-element canvas (NF231), 500+ element responsiveness (NF218), $<$100KB storage (NF242), WCAG keyboard navigation (NF213), and atomic save/export (NF215, NF241). Added a Reference column linking each criterion to its NF requirement. \\
\midrule
Team 2 (peer review, SRS) &
  S.1 defined components (Frontend User Interface, Canvas Manager, Backend Logic and API Layer) that had no corresponding S.2 sections, while S.2 had sections (Editor, Collaboration and Export) not present in S.1. S.2.7 ``Basis for Design'' was also numbered as a component section despite not being a component. &
  Updated S.1 to list exactly the six components covered by S.2.1--S.2.6 (Editor, Shortcut Command Processor, Rendering Engine, Document Management, Configuration and Customization, Collaboration and Export), with cross-references to the corresponding S.2 section. Added a note to S.2.7 clarifying it is an informational supplement, not a component section. S.2 section names and requirement IDs were left unchanged to avoid cascading updates to the HA and VnV plan. \\
\midrule
Team 23 (peer review, HA) &
  HA revision history table contained placeholder entries (``Date1,'' ``Name(s),'' ``Description of changes'') with no actual version tracking. &
  Replaced placeholders with a single final-revision entry dated Apr.\ 6, 2026, listing all team members (Ethan Patterson, Hussain Muhammed, Jeffrey Doan, Kevin Zhu, Chengze Zhao). SRS control table updated similarly with V2 dated Apr.\ 6, 2026. \\
\midrule
Team 2 (peer review, SRS) &
  First-person language (``we,'' ``our,'' ``us'') was used throughout the SRS, making it unsuitable for use by an external team. &
  Replaced all first-person language across: intro.adoc, G3.adoc, P2.adoc, P4.adoc, P6.adoc, E3.adoc, E4.adoc. The academic integrity statement (integrity.adoc) was left unchanged as it is a first-person pledge by convention. \\
\midrule
Team 2 (peer review, SRS) &
  E.4 assumption stated ``User is understanding of how to download/install basic windows programs,'' implying Windows-only support, but G.6 contains no such OS limitation and NF213 explicitly targets Windows, macOS, and Linux. &
  Reworded the E.4 assumption to ``User is able to download and install applications on their operating system,'' generalising it to all supported OSes (Windows, macOS, Linux). \\
\midrule
Team 19 (peer review, SRS) &
  NF214, NF215, NF216, NF217, NF218 were referenced in S.5.2 and S.5.4 but never defined in any S.2.x section, making it impossible to find their full description. &
  Added definitions for all five requirements in their most appropriate S.2.x sections: NF214 (discoverability) and NF217 (visual consistency) added to S.2.1; NF215 (atomic file integrity) added to S.2.4; NF216 (no background network traffic) added to S.2.5; NF218 (large-document responsiveness) added to S.2.3. IDs for NF215, NF216, and NF218 do not follow the section-numbering convention (they start with ``21'' or ``21''/``21''); they were kept as-is to avoid cascading changes to the VnV plan which already references them. \\
\midrule
Team 19 (peer review, SRS) &
  NF231 used unmeasurable terms ``active usage time'' and ``typical workloads,'' making the 60fps requirement untestable. NF242 required ``minimal disk space'' with no quantitative threshold. &
  NF231 updated to: 60fps for at least 95\% of the time during continuous user interaction (typing, dragging, panning) on a canvas with up to 100 elements. NF242 updated to: a note with up to 1000 words and 10 shapes shall occupy less than 100KB on disk. \\
\midrule
Team 2 (peer review, SRS) &
  In S.5.2 the descriptions for NF211 and NF212 were swapped relative to their S.2.1 definitions: NF211 was labelled ``Low-latency input ($\leq$30ms)'' and NF212 was labelled ``Local data persistence and autosave.'' This introduced a false latency inconsistency (30ms vs 50ms) and misplaced NF212 under save/autosave in S.5.4 and S.5.5. &
  Corrected S.5.2 descriptions to match S.2.1: NF211 = usability/clean layout; NF212 = canvas responsiveness $<$50ms. Removed NF212 from the ``Local save/load and autosave'' group in S.5.4. Updated S.5.5 traceability rows for NF211 and NF212 to reflect their correct definitions. The 30ms figure belongs to NF221 (command input) and is a distinct, unrelated requirement. \\
\midrule
Team 23 (peer review, SRS) &
  Acronyms API, CI, UI, MVP, UAT, WCAG, OS, PDF, PNG, GPU, and RAM were used throughout the SRS without being defined in the E.1 Glossary. The existing glossary covered only Vim, UI/UX, PoC, UML, V\&V, and SRS. &
  Added definitions for all missing acronyms to E.1: API (Application Programming Interface), CI (Continuous Integration), UI (User Interface), MVP (Minimum Viable Product), UAT (User Acceptance Testing), WCAG (Web Content Accessibility Guidelines), OS (Operating System), PDF (Portable Document Format), PNG (Portable Network Graphics), GPU (Graphics Processing Unit), RAM (Random Access Memory). Also corrected a typo in the SRS entry (``develoment'' $\to$ ``development''). \\
\midrule
Team 23 (peer review, SRS) &
  NF221 ($\leq$30ms command dispatch) and NF212 ($\leq$50ms canvas response) appeared to conflict for commands that both execute a shortcut and update the canvas (e.g., move shape). Additionally, NF231 still used unmeasurable terms ``active usage time'' and ``typical workloads.'' &
  Clarified NF221 to state it measures command interpretation and dispatch only; added an explicit note that for commands triggering a canvas update, NF212 ($\leq$50ms) is the binding end-to-end input-to-visual-feedback constraint. Updated NF231 to replace ``active usage time under typical workloads'' with ``continuous user interaction (typing, dragging, panning) on a canvas containing up to 100 mixed elements (text and shapes).'' \\
\midrule
Team 23 (peer review, SRS) &
  S.5.1 prioritization table listed F216 (pan and zoom canvas) as ``Medium'' despite G.4 naming panning as a core project goal, and listed F219 (undo/redo) as ``Medium'' despite undo/redo being critical for a modal keyboard-driven editor where actions are rapid. &
  Raised F216 priority to High with rationale referencing G.4. Raised F219 priority to High with rationale that rapid, irreversible keyboard actions make undo/redo essential for preventing data loss and user frustration. Updated S.5.4 summary: moved F216 into the High group alongside F211--F215, and moved F219 into the High group alongside F217 and NF215. Removed F216 from the Medium group. \\
\midrule
Team 19 (peer review, SRS) &
  S.3 contained a full ``Canvas Manager Interface'' section (S.3.4) with detailed inter-component communication specifications, but Canvas Manager was absent from both S.1 (component list) and S.2 (functionality), creating an inconsistency between the environment/context view and the system specification. &
  Added S.2.2 (Canvas Manager) to S.2 with functional requirements F216 (reposition and resize elements) and F217 (canvas navigation), and non-functional requirement NF212 (canvas responsiveness $<$50ms), relocated from S.2.1 Editor where they were misattributed. Requirement IDs F216, F217, and NF212 were retained unchanged to avoid cascading updates to the HA and VnV plan. S.1 component list updated to include Canvas Manager with a cross-reference to S.2.2. Subsequent S.2 section numbers shifted by one: Shortcut Command Processor S.2.2$\to$S.2.3, Rendering Engine S.2.3$\to$S.2.4, Document Management S.2.4$\to$S.2.5, Configuration and Customization S.2.5$\to$S.2.6, Collaboration and Export S.2.6$\to$S.2.7, and Basis for Design S.2.7$\to$S.2.8. \\
\end{tabularx}

\subsection{Design and Design Documentation}

\begin{table}[H]
\centering
\begin{tabularx}{\textwidth}{p{1.3cm} l X X}
\toprule
Issue Number & Reviewer & Given Feedback (Summarized) & Change made  \\
\midrule
\href{https://github.com/ritual-17/flow/issues/282}{282} & Peer &  Missing Module Secrets for Several Modules & Added to the MG to make it clearer why some modules have secrets\\

\href{https://github.com/ritual-17/flow/issues/283}{283} & Peer & Too low level implementation details & Removed mentions to specific technologies over more general ideas
.\\

\href{https://github.com/ritual-17/flow/issues/284}{284} & Peer & M14 modify() Has No Parameters
& Reworked the modify function to have an input to be less confusing \\

\href{https://github.com/ritual-17/flow/issues/285}{285} & Peer & Missing Relationship Between Modules and SRS & Added a description of the requirements to better explain how modules satisfy requirements.\\

\href{https://github.com/ritual-17/flow/issues/286}{286} & Peer & Inconsistent Terminology Across Modules & Changed some of the terminology in the MIS to better match the MG. \\

\href{https://github.com/ritual-17/flow/issues/287}{287} & Peer & Overlapping Module Responsibilities & Clarified many of the modules by adding inputs and expanding outputs, making it less confusing what responsibilities each modules has.\\

\bottomrule
\end{tabularx}
\caption{Traceability between feedback and changes for the Design Docs (Part 1)}
\end{table}

\begin{table}[H]
\centering
\begin{tabularx}{\textwidth}{p{1.3cm} l X X}
\toprule
Issue Number & Reviewer & Given Feedback (Summarized) & Change made  \\
\midrule
\href{https://github.com/ritual-17/flow/issues/525}{525} & TA & Some missing information on types of inputs/outputs. Examples:
In Section 8 for the save function, is success a Boolean or something else? Don't leave it to someone else to assume it's a boolean.
 & Added data type to outputs. \\

\href{https://github.com/ritual-17/flow/issues/525}{525} & TA &
More complicated data structures such as Sets and Stacks are used but are not described in Section 4
 & Added sets and Stacks to Section 4 \\

\href{https://github.com/ritual-17/flow/issues/525}{525} & TA & Some functions do not have output and do not modify any observable state, but they seem like they should, such as shape-moving functions.
 & mentioned if changes could be observable via other modules due to display.
F213 \\

\href{https://github.com/ritual-17/flow/issues/525}{525} & TA & Some functions have underspecified inputs, such as Section 17's resize function which only takes a GeometryID but not the resize factor.
& Specified all inputs \\

\href{https://github.com/ritual-17/flow/issues/525}{525} & TA & How are inverses defined with respect to commands in the undo-redo module?
& Defined how the inverses of commands would work. \\

\bottomrule
\end{tabularx}
\caption{Traceability between feedback and changes for the Design Docs Plan (Part 2)}
\end{table}


\subsection{VnV Plan and Report}

\begin{table}[H]
\centering
\begin{tabularx}{\textwidth}{p{1.3cm} l X X}
\toprule
Issue Number & Reviewer & Given Feedback (Summarized) & Change made  \\
\midrule
\href{https://github.com/ritual-17/flow/issues/228}{228} & Peer & "Nonfunctional tests lack measurable criteria" & NF tests list in the
VnV plan were made a bit more specific \\
\href{https://github.com/ritual-17/flow/issues/231}{231} & Peer & NFR Tests 211 and 218 both measure same performance and latency
requirements but only differ in scale & No change made in documentation.
Difference of scale represents different scenarios, with smaller scale
having higher priority as it represents typical usage scenarios \\
\href{https://github.com/ritual-17/flow/issues/232}{232} & Peer & Usability survey lists questions but doesn't specify concrete success metrics
& Survey questions have been updated and refined \\
\href{https://github.com/ritual-17/flow/issues/233}{233} & Peer & Testing tools not specified & No change made in documentation.
Jest and Playwright were the mentioned tools in VnV Plan, justification also provided \\
\href{https://github.com/ritual-17/flow/issues/234}{234} & Peer & Usability survey lacks measurable criteria & survey questions have been
updated and refined \\
\bottomrule
\end{tabularx}
\caption{Traceability between feedback and changes for the VnV Plan (Part 1)}
\end{table}

\begin{table}[H]
\centering
\begin{tabularx}{\textwidth}{p{1.3cm} l X X}
\toprule
Issue Number & Reviewer & Given Feedback (Summarized) & Change made  \\
\midrule
\href{https://github.com/ritual-17/flow/issues/529}{529} & TA & list of tables is missing in VnV Plan & list of tables added back to document \\
\href{https://github.com/ritual-17/flow/issues/529}{529} & TA & NFR testing not specific enough. For example, NF216 is a code review
 on parts that use network data. What kind of code review is expected? & NF tests,
 including NF216, were made more specific \\
\href{https://github.com/ritual-17/flow/issues/529}{529} & TA & Redundancy. For example, F213 is a relatively straightforward test to include.
It could feasibly be included into "Area of Testing1". & Added Functional test for
F213 \\
\href{https://github.com/ritual-17/flow/issues/529}{529} & TA & Be more specific and intentional about nondynamic testing. Provide
justification for inclusion or a brief checklist or plan for nondynamic testing.
& Justification for nondynamic testing added to VnV Plan \\
\bottomrule
\end{tabularx}
\caption{Traceability between feedback and changes for the VnV Plan (Part 2)}
\end{table}

To summarize the table(s) above, the feedback we received on the VnV Plan was primarily
focused on improving the specificity of our nonfunctional tests, ensuring that we included
a list of tables in the document, and addressing redundancy in our testing plan. Overall,
we made changes to our VnV Plan to address each of these points, resulting in a more
comprehensive and well-structured testing strategy for our project.

\begin{table}[H]
\centering
\begin{tabularx}{\textwidth}{p{1.3cm} l X X}
\toprule
Issue Number & Reviewer & Given Feedback (Summarized) & Change made  \\
\midrule
\href{https://github.com/ritual-17/flow/issues/477}{477} & Peer & No discussion of timeline to implement M3 & Added description of timeline
for M3 implementation \\
\href{https://github.com/ritual-17/flow/issues/473}{473} & Peer & Code coverage short of planned target, with no explanation & Added
explanation addressing the low code coverage \\
\href{https://github.com/ritual-17/flow/issues/475}{475} & Peer & Unit test section has no reults summary & No changes made to the
documentation. Tests were described in the VnV Plan \\
\href{https://github.com/ritual-17/flow/issues/476}{476} & Peer & Only two usability test participants, with no justification & This has been
addressed. A plan and desire for an increase in sample size was mentioned  \\
\href{https://github.com/ritual-17/flow/issues/474}{474} & Peer & Inconsistent usability conclusions & No changes made to the documentation.
An explanation to the peer on the consistency of our conclusions was provided \\
\href{https://github.com/ritual-17/flow/issues/478}{478} & Peer & Flow's comparison to existing implementation lacked support & The validity
of Flow over other solutions was emphasized with more detailed justifications. \\
\href{https://github.com/ritual-17/flow/issues/532}{532} & TA & Section 3 and 4 does not mention what requirements are involved in the tests
& explicitly mentioned which requirements involved in tests  \\
\href{https://github.com/ritual-17/flow/issues/532}{532} & TA & Usability description lacked explanation and/or acknowledgement of small
sample size & This has been addressed. A plan and desire for an increase in sample
size was mentioned  \\
\href{https://github.com/ritual-17/flow/issues/532}{532} & TA & Performance data could be presented better & improved presentation of
performance data. Provided further explaination and justification of test. \\
\bottomrule
\end{tabularx}
\caption{Traceability between feedback and changes for the VnV Report.}
\end{table}

In summary, we received feedback from our peers and TA regarding the VnV Report.
The feedback from our peers had to do with the lack of explanation for our code
coverage, and the consistency of our conclusions. The feedback from our TA
related more to the lack of mention of requirements in our tests, and the
explanations of some data items. We have addressed all of this feedback in our
VnV Report, and we have provided explanations and justifications where necessary.

\section{Extras}

% \plt{Summarize the extras that were tackled by this project.  Extras
% can include usability testing, code walkthroughs, user documentation, formal
% proof, GenderMag personas, Design Thinking, etc.  Extras should have already
% been approved by the course instructor as included in your problem statement.}

\begin{itemize}
\item \textbf{Usability Testing:} An informal yet structured usability test was 
conducted with students representing the target user demographic. The test aimed 
to assess the intuitiveness and efficiency of Flow's user interface and 
workflows. To ensure systematic and objective evaluation, participants performed 
predefined tasks, such as creating and organizing notes, and inserting and 
editing diagrams. Performance metrics, including task completion times, were 
recorded. Following the test, participants provided feedback on their experience, 
highlighting any difficulties and suggesting improvements.

\item \textbf{User Manual:} A comprehensive user manual was developed to assist 
new users in navigating Flow's features and functionalities. The manual provides 
step-by-step instructions for creating, editing, and managing notes and diagrams,
along with explanations of the various tools and keyboard shortcuts. It functions 
as both a user support resource and a validation tool to confirm that all 
features are accessible and understandable.
\end{itemize}

\section{Design Iteration (LO11 (PrototypeIterate))}

\plt{Explain how you arrived at your final design and implementation.  How did
the design evolve from the first version to the final version?}

\plt{Don't just say what you changed, say why you changed it.  The needs of the
client should be part of the explanation.  For example, if you made changes in
response to usability testing, explain what the testing found and what changes
it led to.}
% \plt{Explain how you arrived at your final design and implementation.  How did
% the design evolve from the first version to the final version?}
%
% \plt{Don't just say what you changed, say why you changed it.  The needs of the
% client should be part of the explanation.  For example, if you made changes in
% response to usability testing, explain what the testing found and what changes
% it led to.}

Many things changed in the final design compared to the initial design. One
original requirement we had was to have no text to visual based rendering
system. We wanted Flow to be fully canvas-based, meaning that there was no
underlying text the user would modify to change what is displayed on the screen
(like UML for example). This requirement held for shapes, but it was clear for
text-based notes involving complex math notation, existing solutions just made
more sense. We wanted to balance speed with intuitiveness for the user. This is
where we introduced Typst integration, which does have a render step, but
fits well alongside the flow of the rest of the app.

We also made changes based on user testing. Testing made it clear that although
the system makes sense, it has quite a steep learning curve. To address this,
we added a help menu that users can access from any mode to display the
available commands for that mode. We also kept the mode transition keybinds at
the top as that was a common area of friction during user testing.

Overall, the approach to the development of Flow was very incremental. Through
test usage in our own lectures this term, we identified areas of improvement
and implemented solutions for them. This included but was not limited to bug
fixes, intuitive transitions between modes (e.g. line to anchor line mode),
shape position on insertions, allowing multiple ways to pan the infinite
canvas, and various quality of life improvements.

\section{Design Decisions (LO12)}

\begin{itemize}
  \item Our design choices were driven by the need to support math-related note-taking
    with a fast, responsive authoring experience. Using Typst allowed us to support
    structured mathematical typesetting directly in the editor while still keeping the
    application lightweight. The app compiles Typst content locally through the Electron
    main process, producing SVG output in real time so students can see rendered math
    immediately without waiting on a remote service.

  \item Limitations influenced the architecture in several ways. Because students use
    different devices and situations, we chose Electron to deliver a cross-platform
    desktop app that works on Windows, macOS, and Linux. Electron also gives us direct
    access to the local file system for import/export and PDF handling, which is important
    for an academic note-taking tool. A local desktop app avoids browser permission and
    network dependency issues of a web app, supports offline use, and reduces unnecessary
    complexity when the goal is reliable note capture rather than cloud collaboration.

  \item We assumed users would want a fast, keyboard-driven interface and that the main
    value of the application would be quick note creation rather than graphical menu
    navigation. That assumption drove the modal design: the app uses distinct modes such as
    normal, insert, visual, text, line, and anchor-line to keep the command space manageable.
    This lets the editor support a rich feature set — shape creation, line editing, text box
    insertion, PDF slide import/export, and Typst rendering — without overwhelming the user
    with too many simultaneous shortcuts.

  \item Constraints such as limited physical keys and the need for advanced diagram editing
    shaped our keybinding strategy. The diagram editing tool requires many discrete actions,
    so we did not try to cram everything into a single flat shortcut layer. Instead, we
    grouped actions into mode-specific contexts and reused familiar navigation keys like hjkl
    and arrow keys. This keeps interactions intuitive and reduces the mental load of
    remembering commands while still allowing powerful editing workflows for geometric shapes,
    auto-linking, and line-based diagram construction.
\end{itemize}

\section{Economic Considerations (LO23)}

% \plt{Is there a market for your product? What would be involved in marketing your 
% product? What is your estimate of the cost to produce a version that you could 
% sell?  What would you charge for your product?  How many units would you have to 
% sell to make money? If your product isn't something that would be sold, like an 
% open source project, how would you go about attracting users?  How many potential 
% users currently exist?}

There is likely a market for Flow, especially among engineering  and computer 
science students, and technical professionals who regularly create diagrams, 
structured notes, circuits, flowcharts, or annotated lecture content. Current 
note-taking tools often force users to choose between strong text editing, 
strong handwriting support, or strong diagramming support. Flow aims to combine 
structured text input, diagramming, keyboard-driven workflows, and flexible 
positioning into one application. It would compete with tools such as Microsoft 
OneNote, GoodNotes, Typst, Google Docs, and more. 

Our usability testing suggests that Flow is strongest for diagram-heavy 
workflows, circuit design, structured layouts, and keyboard-driven note-taking 
rather than purely handwritten or text-heavy notes. Therefore, our marketing efforts
would likely focus on engineering and technical students and professionals.

\vspace{0.5em}

Marketing Flow would likely involve:
\begin{itemize}
\item Demonstrations targeted toward engineering and STEM students
\item Short tutorial videos showing keyboard-based workflows
\item Comparisons against existing tools for diagrams and note-taking
\item University club partnerships and campus ambassadors
\item Social media content showing real use cases such as lecture notes, circuits,
 flowcharts, and annotated PDFs
\end{itemize}

\vspace{0.5em}

If Flow were developed into a commercial product, an early version could likely 
be built and maintained by a small team of 3-5 developers. Estimated costs for a 
polished sellable version could include:
\begin{itemize}
\item Development costs: approximately \$50,000-\$150,000
\item Hosting and cloud infrastructure: approximately \$500-\$2,000 per month
\item Marketing costs: approximately \$5,000-\$20,000 initially
\item Ongoing maintenance and feature development costs
\end{itemize}

\vspace{0.5em}

These estimates are rough. They are based on typical salaries for software 
developers, costs for cloud services, and marketing expenses for a small software 
product.

\vspace{0.5em}

A reasonable pricing model for Flow would likely be:
\begin{itemize}
\item Free version with basic note-taking and diagramming
\item Student plan around \$3-\$5 per month
\item Professional plan around \$8-\$12 per month
\item One-time educational license for universities or departments
\end{itemize}
This pricing model is based on the value provided by Flow, the competitive 
landscape, and typical pricing for productivity software. If the average user 
paid approximately \$5 per month, and the product cost roughly \$100,000 to build, 
then Flow would need approximately 1,700 annual subscribers to recover its 
initial development costs within one year. 

At this point, Flow is more likely to be an open-source project than a commercial
product. To attract users to an open-source project, we would likely focus on:
\begin{itemize}
\item GitHub visibility
\item Strong documentation and tutorials
\item Student communities
\item Technical blogs and YouTube demonstrations
\item Contributions from users who want new features or integrations
\end{itemize}

\vspace{0.5em}

Overall, There are potentially millions of users who could benefit from a tool 
like Flow, including university students, engineers, developers, technical writers,
and more. The success of other note-taking and diagramming products shows there is 
already a large audience looking for better workflows and more flexible tools. With 
the right marketing and continued development, Flow could attract a significant 
user base over time.

\section{Reflection on Project Management (LO24)}


\subsection{How Does Your Project Management Compare to Your Development Plan}

\plt{Did you follow your Development plan, with respect to the team meeting plan,
team communication plan, team member roles and workflow plan.  Did you use the
technology you planned on using?}

\subsection{What Went Well?}

\plt{What went well for your project management in terms of processes and
technology?}
For the most part the team stuck to the plan. The milestone structure held up well --- each deliverable (SRS, HA, VnV Plan, Design Doc, Rev 0 demo) landed close to the scheduled date, and the defined roles (team lead, meeting chair, keynoter, liaison, lead reviewer) were respected throughout. GitHub was used for all code changes via pull requests and issue tracking, which matched the planned workflow. Communication happened primarily over Discord with occasional Microsoft Teams calls for longer planning sessions, also consistent with the plan.

The main deviation was in feature scope. The development plan assumed authentication and cloud sync would be tackled in Milestone 6, but those were dropped early once it became clear the core Vim-modal canvas interaction was more complex than estimated. The final product stayed local-only, which is reflected in the SRS but was not the original intent.

\subsection{What Went Well?}

The GitHub workflow was probably the strongest part of the process. Having every change go through a pull request, with at least one review before merge, caught a fair number of bugs and kept the codebase reasonably consistent. The issue tracker also doubled as a log of decisions and feedback responses, which made preparing the traceability document much easier than it would have been otherwise.

Role clarity helped too. Knowing who was the primary contact for TAs, who chaired meetings, and who owned the final review pass meant those things actually happened instead of falling through the cracks in a five-person team.

\subsection{What Went Wrong?}

Time estimation for the keyboard interaction layer was consistently off. Implementing Vim-style modal editing on a canvas is not the same as implementing it in a text editor, and the team underestimated how much of the codebase that would touch. As a result, document persistence features (save, load, version history) were not implemented by Rev 0 --- they were specced out in the SRS but the system ran entirely in memory for the demo.

Documentation consistency was also a recurring issue. Because multiple people were writing different sections independently, terminology and requirement IDs drifted across documents. This created a non-trivial cleanup effort during the Rev 1 pass, particularly around the SRS and Hazard Analysis.

\subsection{What Would you Do Differently Next Time?}

Start integration earlier. The team worked on components fairly independently and only put them together properly close to demo time. Earlier integration would have surfaced the harder cross-component problems (e.g., how the shortcut processor interacts with the canvas model) before they became blocking issues.

On the documentation side, a shared glossary and requirement ID convention agreed on at the start would have saved time. A lot of the Rev 1 SRS work was fixing inconsistencies that would not have existed if there had been a brief alignment session before writing began.

\section{Ethics and Equity (LO18)}

 % \plt{Describe how your team applied the principle of equity and universal         design
 % to ensure equitable treatment of all stakeholders.}

Our team applied the principle of equity and universal design in many ways throughout 
the project. Our project originally stared as an way to ensure that people who don't have 
a touch screen can still take notes in class, even if there is not enough space for a full 
keyboard and mouse. To this end our project focuses much more on keyboard inputs as there 
are other options for touch-screen and mouse. Our group also did usability testing to 
ensure that we have good universal design. This is so the main stakeholder group(people 
who want to take notes in class with keyboard) are able to use Flow  regardless of 
needs/experience. This led to us adding things like the status bar to show users their 
current mode \& position and the command menu to list commands so the user can always know 
what they need to press. We also considered some other ways of making Flow more accessible 
such as supporting voice commands and allowing custom keybinds/themes. As we wanted to get 
the main functionality of the program first, these are currently extras. But we 
considered them along with other accessibly options that would help everyone like the 
command menu. 


\section{Reflection on Capstone}


\subsection{Which Courses Were Relevant}

SFWRENG 3RA3 (Software Requirements and Security Considerations) was the most directly applicable --- the SRS process, hazard analysis, security requirements, and traceability all came directly from that course. SFWRENG 3A04 (Software Design III: Large System Design) was relevant for thinking about component architecture, architectural styles, and interface design between subsystems. On the systems side, SFWRENG 3SH3 (Operating Systems) gave useful background for understanding file I/O, process lifecycle, and the implications of Electron running a Node.js main process alongside a renderer process. SFWRENG 4HC3 (Human-Computer Interfaces) informed decisions around keyboard-first interaction design and usability evaluation.

\subsection{Knowledge/Skills Outside of Courses}

Electron and its main/renderer process architecture was not covered in any course and required learning from scratch. The team also had to get familiar with TypeScript at a practical level beyond what was taught, particularly around type-safe event handling between processes. The biggest skill gap was Vim's modal editing model --- understanding how to implement mode transitions, command composition, and a proper operator-motion grammar took significant self-directed learning before any code could be written for it.

\end{document}
