\documentclass[12pt, titlepage]{article}

\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=red,
    urlcolor=blue
}
\usepackage[round]{natbib}

\input{../Comments}
\input{../Common}

\begin{document}

\title{Verification and Validation Report: \progname}
\author{\authname}
\date{\today}

\maketitle

\pagenumbering{roman}

\section{Revision History}

\begin{tabularx}{\textwidth}{p{3cm}p{2cm}X}
\toprule {\bf Date} & {\bf Version} & {\bf Notes}\\
\midrule
Date 1 & 1.0 & Notes\\
Date 2 & 1.1 & Notes\\
\bottomrule
\end{tabularx}

~\newpage

\section{Symbols, Abbreviations and Acronyms}

\renewcommand{\arraystretch}{1.2}
\begin{tabular}{l l}
  \toprule
  \textbf{symbol} & \textbf{description}\\
  \midrule
  T & Test\\
  \bottomrule
\end{tabular}\\

\wss{symbols, abbreviations or acronyms -- you can reference the SRS tables if needed}

\newpage

\tableofcontents

\listoftables %if appropriate

\listoffigures %if appropriate

\newpage

\pagenumbering{arabic}

This document ...

\section{Functional Requirements Evaluation}
\setlength{\parindent}{0pt}

\subsection{Functional User Testing}
User testing was conducted to evaluate whether the implemented editing and
canvas manipulation functionality satisfies the functional requirements
specified in the SRS. Participants were asked to perform a series of diagram
creation tasks using Flow for the first time. These tasks involved inserting
shapes, connecting elements with lines, and positioning objects on the
canvas using the keyboard-driven interaction model.

\vspace{1em}

Two participants completed the testing procedure. Each participant performed
the same task twice in order to observe how performance changed after gaining
familiarity with the interface.

\vspace{1em}

The first participant completed the task in approximately 3 minutes and
7 seconds during the first run and made roughly ten errors. Most of these
errors occurred because the participant was initially unaware that they could
switch between line mode and anchor-line mode in order to continue the same
line between shapes. After becoming familiar with this behavior, the
participant completed the second run in approximately 1 minute and 49 seconds
with only one or two minor errors.

\vspace{1em}

The second participant required approximately 8 minutes and 46 seconds to
complete the first run and approximately 6 minutes and 23 seconds for the
second run. During these runs, the participant performed several accidental
operations that required undo actions and occasionally forgot how to execute
specific commands, such as adding text to a shape or switching interaction
modes.

\vspace{1em}

Despite these initial usability challenges, both participants were able to
successfully complete the required diagram creation tasks. The reduction in
completion time between runs suggests that users become more efficient after
a short familiarization period with the keyboard-driven workflow.

\vspace{1em}

\begin{table}[h]
\centering
\begin{tabular}{c c c c}
\toprule
Participant & Run & Completion Time & Errors / Issues \\
\midrule
User 1 & Run 1 & 3:07 & $\sim$10 errors \\
User 1 & Run 2 & 1:49 & 1--2 errors \\
User 2 & Run 1 & 8:46 & 2 undo, 3 command issues \\
User 2 & Run 2 & 6:23 & 3 undo, 3 command issues \\
\bottomrule
\end{tabular}
\caption{Summary of Functional User Testing Results}
\end{table}


\vspace{1em}

Overall, the testing results indicate that the implemented editing and canvas
manipulation functionality operates as intended. Users were able to create
and manipulate diagram elements and complete the assigned tasks successfully.
However, the tests also reveal that the keyboard-driven interface introduces
a learning curve for first-time users, particularly when remembering
available commands and interaction modes.


\subsection{User Feedback}

After completing the testing tasks, participants were asked a series of
questions about their experience using Flow. The goal of these questions was
to evaluate how intuitive the system felt to first-time users and to identify
areas where the interaction design could be improved.

\vspace{1em}

Participants highlighted the line creation mode as one of the most effective
features of the system. In particular, the automatic snapping behavior and
the ability to extend connections between shapes without manually selecting
connection points were viewed as highly convenient when constructing
diagram structures. Users also noted that positioning elements on the canvas
felt intuitive compared to text-based diagram tools.

\vspace{1em}

Several usability challenges were also identified during testing. Both users
reported difficulty remembering all available keyboard shortcuts during
their initial interaction with the system. One participant suggested that a
reference sheet or command palette could help users discover available
commands more easily.

\vspace{1em}

Participants also suggested several potential feature improvements,
including support for inserting custom icons, automatic linking of shapes
during diagram creation, and the ability to select all elements on the
canvas. These suggestions indicate potential directions for future
development that could further improve the usability and flexibility of the
system.

\vspace{1em}

Overall, the feedback suggests that Flow's keyboard-driven interaction model
is powerful for diagram construction, but additional discoverability features
may be beneficial to reduce the learning curve for new users.

\subsection{Summary}

The functional evaluation demonstrates that the core diagram creation and
editing capabilities of Flow operate as intended. All participants were able
to successfully complete the assigned tasks using the implemented features,
confirming that the system satisfies the primary functional requirements
related to canvas editing and diagram manipulation.
\vspace{1em}

The testing results also show that user efficiency improves noticeably after
a short familiarization period. Completion times decreased between the first
and second runs for both participants, suggesting that the keyboard-based
interaction model becomes more efficient once users become comfortable with
the available commands.

\vspace{1em}

While the core functionality performed correctly, the evaluation also
identified usability challenges for first-time users. In particular,
participants experienced difficulty remembering keyboard shortcuts and
distinguishing between certain interaction modes. These observations suggest
that improved command discoverability and documentation could further
enhance the user experience.

\vspace{1em}

Overall, the implemented system successfully meets the functional goals
outlined in the SRS while also revealing opportunities for future usability
improvements.

\section{Nonfunctional Requirements Evaluation}

\subsection{Usability}

\subsection{Performance}

\subsection{etc.}

\section{Comparison to Existing Implementation}
\setlength{\parindent}{0pt}
% This section will not be appropriate for every project.

\subsection{Pen and Paper}

Pen-and-paper note taking allows quick sketches and diagrams, but it lacks digital
advantages such as editing, sharing, and organization. Notes cannot easily be
rearranged or modified without rewriting large portions.

\vspace{1em}

The Flow prototype improves on this by allowing users to freely edit diagrams and
text on a digital canvas. Shapes and text boxes can be moved, resized, and modified
without recreating the content. This allows iterative editing that is not possible
with traditional handwritten notes.

\subsection{Tablet-Based Note Taking}

Tablet systems such as the iPad with Apple Pencil allow freehand diagramming and
handwritten notes. While flexible, these solutions require specialized hardware and
often rely on handwriting input, which may be slower than typing for many users.

\vspace{1em}

Flow instead targets keyboard-based workflows and runs on standard desktop computers.
The prototype demonstrates keyboard-driven editing and diagram manipulation, allowing
users to create structured notes and diagrams without requiring additional hardware.

\subsection{Traditional Text Editors}

Applications such as Microsoft Word or Google Docs support structured text editing
but provide limited support for integrated diagram creation. Diagrams often require
external tools or inserted images.

\vspace{1em}

The Flow prototype integrates diagram creation directly into the editing workspace.
Users can insert geometric shapes and connect them with arrows directly on the canvas
while simultaneously editing text content. This removes the need to switch between separate
diagramming tools.

\subsection{Mouse-Driven Diagram Editors}

Tools such as Draw.io or OneNote allow diagram creation but rely heavily on mouse-based
interaction and menu navigation. Creating shapes or connections often requires multiple UI interactions.

\vspace{1em}

Flow differs by emphasizing keyboard-driven interaction. The current prototype demonstrates
Vim-style navigation and keyboard commands that allow users to manipulate shapes, text boxes,
and diagram elements without relying on extensive mouse interaction.

\subsection{Text-Based Diagram Languages}

Diagram languages such as Mermaid or PlantUML allow diagrams to be described using text. While
powerful, they require a separate compilation or rendering step to visualize the diagram.

\vspace{1em}

Flow eliminates this separation by providing direct manipulation of diagram elements on the
canvas. The rendering engine updates the diagram in real time as the user edits elements, avoiding
the write–compile–preview workflow required by text-based diagram languages.

\subsection{Document Markup Languages}

Document preparation systems such as \LaTeX{} or Typst support complex document layouts and diagram
generation. However, these systems rely on writing structured markup code and are typically designed
for page-based documents rather than an interactive canvas.

\vspace{1em}

Flow instead uses a canvas-based editing environment where diagram elements and text boxes can be
freely positioned. The prototype supports interactive editing of shapes and text elements, which allows
users to experiment with diagram layouts more quickly than code-based document systems.

\subsection{Summary}

The Flow prototype demonstrates that a keyboard-driven, canvas-based note-taking system can combine
advantages from multiple existing approaches. Compared to existing tools, the system:

\begin{itemize}
\item Integrates text editing and diagram creation in a single interface
\item Supports keyboard-driven workflows inspired by Vim
\item Allows direct manipulation of diagram elements without compilation or external tools
\item Provides a flexible canvas for positioning text and diagrams
\end{itemize}

Although the current implementation does not yet include persistent storage, exporting, or collaboration
features, the prototype validates the feasibility of the core interaction model and demonstrates improvements
over several existing approaches.


\section{Unit Testing}

\section{Changes Due to Testing}

Following the Rev 0 demonstration, comprehensive feedback was received
from both the course professor and teaching assistant. This feedback
directly influenced the project's direction and implementation
priorities, resulting in significant improvements to the system's
design, usability planning, and development approach. Additionally,
usability tests were conducted with outside users to gather real-world
insights and further improve the product based on actual user interactions.

\subsection{Feedback Summary}

\subsubsection{Professor Feedback}
The professor provided detailed feedback during Rev 0 highlighting both strengths
and areas for improvement:

\begin{itemize}
\item \textbf{Positive Recognition}: The demonstration effectively
  showcased the classroom note-taking concept, representing a
  significant improvement over the Proof of Concept demo. The project
  vision was described as "exciting to see come together."

\item \textbf{Productivity Report Enhancement}: The demo plan section
  in the productivity report required more detailed planning and
  structure, similar to the presentation format.

\item \textbf{Usability Testing Planning}: Emphasized the critical
  importance of comprehensive usability testing, requiring detailed
  planning addressing who, when, where, what, and how aspects. Specific
  guidance included:
  \begin{itemize}
  \item \textbf{What}: Define specific tasks for test subjects to
    perform
  \item \textbf{How}: Establish clear metrics for measuring usability,
    likely focusing on user interviews
  \item \textbf{Planning}: Questions should be prepared in advance
  \end{itemize}

\item \textbf{Feature Prioritization}: Recommended implementing PDF
  export functionality as a high priority, while "flow" file saving
  could be deprioritized. Additionally, The team must decide between
  infinite canvas or separate pages for adding additional slides/
  diagrams.
\end{itemize}

\subsubsection{Teaching Assistant Feedback}
The TA provided additional insights complementing the professor's
assessment:

\begin{itemize}
\item \textbf{Demo Quality}: Described the demonstration as "smooth and
  impressive" with much clearer project vision compared to the PoC
  demo.

\item \textbf{Usability Testing Considerations}: Emphasized the
  importance of considering users' prerequisite knowledge (such as Vim
  proficiency) and how this affects test result interpretation.

\item \textbf{Feature Prioritization}: Reinforced the need to prioritize
  features critical to the final demonstration.
\end{itemize}

\subsubsection{User Testing Feedback}
We conducted a usability test with two individuals that have a technical
background, but is not part of the development team. The users were
asked to perform a series of tasks using the current prototype,
and their interactions were observed and recorded.
The users provided the following feedback:

\begin{itemize}
\item \textbf{Auto Linking Mode}: The users suggested that an auto-linking
mode where the system automatically creates a line connection between two
shapes upon object creation. New shapes will automatically connect to the
most recently created shape. This would reduce the number of steps required
to create a diagram and make it easier.

\item \textbf{Select All}: The users requested a "select all" feature that
allows users to select all objects and elements on the canvas with a single
command. A simple feature that would improve the quality of life for users.

\item \textbf{Custom Icons}: The users suggest adding custom icons such as
different circuit symbols and having keybinds such as "ii" to insert an icon
and have fuzzy find a list of available icons.

\item \textbf{Anchor points}: The users suggest adding custom anchor points
when adding a custom icon. This would allow users to specify where the connection
points of their icons are, making it easier to create diagrams that
require custom icons.

\item \textbf{End Remarks and Comparisons}: The user expressed that the current
prototype would be a great product and made a comparison to other circuit makers
in typst which they were not quite fond of. They expressed that the product would
be great at drawing circuits if provided with a few more features listed above.
\end{itemize}

\subsection{Future Changes To Be Implemented in Response to Feedback}

\subsubsection{Architecture Decision: Infinite Canvas vs. Separate Pages}
Following the professor's recommendation, the team conducted an
architectural analysis and is still deciding on a solution.
This decision will be based on:

\begin{itemize}
\item While implementing both solutions would be ideal, we have considered
time constraints as an issue, and would prioritize implementing one
solution over the other.
\item Better alignment with the classroom note-taking workflow. The
infinite canvas would allow users to freely position and organize their notes;
however, the separate pages will help with organization and navigation.
\item In the end, the team decided that we will provide support for uploading
and viewing a PDF slide, whether that be through an infinite canvas,
multiple pages, or both.
\end{itemize}

\subsubsection{PDF Export Implementation}
Prioritizing the professor's recommendation, PDF export functionality
will be implemented as a core feature, allowing users to export their
diagrams in a widely compatible format suitable for sharing and
archiving.

\subsubsection{Work Distribution Improvements}
Addressing the concern about uneven workload distribution, the team
implemented several measures:

\begin{itemize}
\item Clear task assignment and rotation across different project areas
\item Regular code review processes to ensure knowledge sharing
\item Documentation improvements to facilitate team-wide understanding
\end{itemize}

\subsubsection{User Testing Feedback Integration}
Earlier usability testing produced several feature suggestions from
technical users outside the development team. To address these items,
we took the following steps:

\begin{itemize}
\item Prototyping an "auto-linking" mode: new shapes automatically connect to
  the most recently created object, reducing steps to draw diagrams.

\item Adding a global \texttt{select all} command, enabling users to
  highlight every canvas element with one keystroke.

\item Looking into extending the icon insertion system to support custom
  symbols with a fuzzy-find picker and permitted definition of custom
  anchor points for those icons to control connection locations.

\item Implementing miscellaneous quality-of-life tweaks (keyboard hints,
  clearer messages) based on the user's general remarks.

\item Considering additional suggestions (circuit symbol libraries, advanced
  anchoring) in the project backlog for future iterations.
\end{itemize}

\subsection{Changes Already Implemented in Response to Feedback}
The team has already implemented several changes in response to feedback/testing
from internal usage and the POC demo:

\begin{itemize}
\item \textbf{Keybinding Layout}: We have put more thought and effort into the keybinding layout,
ensuring that it is more intuitive and easier to learn for users familiar with Vim-style keybindings.
This was well recieved during user testing and has improved the overall usability of the prototype.

\item \textbf{Visual Indicators}: We have added visual indicators for the different modes users are able
to be in (normal, insert, visual). Now the cursor will change based on the mode, signaling to
the user which mode they are in. This has helped users understand the current state of the application 
and has reduced confusion during interactions. 

\item \textbf{Line Anchor Points}: A small but impactful change was the addition of anchor points for line connections. 
This allows users to connect to created lines instead of just shapes, enabling more complex diagrams and improving the 
flexibility of the system. This was a direct result of internal testing and POC feedback.

\end{itemize}

\subsection{Impact on Project Quality}

The feedback-driven changes significantly enhanced the project's overall
quality:

\begin{itemize}
\item \textbf{Enhanced Architecture}: The infinite canvas and separate
  pages decision provides a more intuitive and flexible user experience
  aligned with the target workflow.

\item \textbf{Increased Robustness}: PDF export functionality addresses
  a critical user requirement for document sharing and archiving.

\item \textbf{Better Team Dynamics}: Improved work distribution ensures
  all team members develop relevant skills and contribute meaningfully
  to the project.

\end{itemize}

The verification and validation process, through structured feedback
collection and responsive implementation, has ensured that the Flow
project evolves based on expert guidance and user needs, resulting in
a higher-quality final product that better serves its intended
educational purpose.
\wss{This section should highlight how feedback from the users and from
the supervisor (when one exists) shaped the final product.  In particular
the feedback from the Rev 0 demo to the supervisor (or to potential users)
should be highlighted.}

\section{Automated Testing}

As outlined in the VnV Plan, we implemented automated testing using the
\texttt{Jest} framework. We also projected the use of \texttt{Playwright} in the
original plan, but as of this report, we have not used it for any testing. Due
to the rapid development and changes made to the app, we have not invested the
time to create end-to-end tests at this point that may be more brittle than
unit tests and slow down development speed. Additionally, usage/integration of
\texttt{Coveralls} was discussed in the plan, but has not been added at this
point due to time constraints and its relatively low priority. We have been
able to use Jest to check code coverage.


Automated tests are run via GitHub Actions and run on every new PR.

\section{Trace to Requirements}

This section provides traceability between the requirements defined in the
Software Requirements Specification (SRS) and the verification activities
performed during testing. Each requirement is linked to one or more test
cases described in the Verification and Validation Plan. The results of the
tests demonstrate whether the implementation satisfies the specified
requirements.

Functional requirements are validated primarily through automated system
tests that simulate user interactions with the application. These tests
verify core functionality such as creating notes, manipulating diagram
elements, and performing file management operations.

Non-functional requirements are evaluated through a combination of manual
tests, usability evaluation, and performance measurements. These tests assess
system responsiveness, usability, cross-platform compatibility, and data
integrity.

Table~\ref{tab:reqTrace} summarizes the mapping between SRS requirements and
the test cases used to verify them.

\begin{table}[htbp]
\centering
\begin{tabular}{p{1.8cm} p{6.8cm} p{2.8cm} p{3.5cm}}
\toprule
\textbf{Req ID} & \textbf{Requirement Description} & \textbf{Test Case} & \textbf{Result} \\
\midrule

F211 & The system shall allow users to create and edit notes. 
& test-F211 & Pass \\

F214 & The system shall allow users to insert and manipulate shapes on the canvas. 
& test-F214 & Pass \\

F217 & The system shall allow users to save and reopen notes. 
& test-F217 & Not Implemented Yet \\

F243 & The system shall allow users to export notes as PDF files. 
& test-F243 & Not Implemented Yet \\

NF211 & The system shall provide low-latency input and rendering during editing operations. 
& test-NF211 & Pass \\

NF218 & The system shall maintain acceptable performance when handling a large number of shapes or objects. 
& test-NF218 & Pass \\

NF213 & The system shall support execution on Windows, macOS, and Linux platforms. 
& test-NF213 & Pass \\

NF214 & The system shall provide accessible keyboard shortcuts for editing operations. 
& test-NF214 & Pass \\

NF217 & The system shall provide an intuitive and consistent user interface. 
& test-NF217 & Pass \\

NF212 & The system shall maintain local data persistence and autosave functionality. 
& test-NF212 & Not Implemented Yet \\

NF215 & The system shall maintain file integrity during save and export operations. 
& test-NF215 & Not Implemented Yet \\

NF216 & The system shall not perform background network communication. 
& test-NF216 & Pass \\

\bottomrule
\end{tabular}
\caption{Traceability Between Requirements and Test Cases}
\label{tab:reqTrace}
\end{table}

The results indicate that all implemented requirements were successfully
verified through the corresponding tests for features that have been implemented 
so far. No critical failures were observed during the verification process, 
demonstrating that the implemented systemsatisfies the functional and non-functional 
requirements specified in the
SRS.

\vspace{25em}
		
\section{Trace to Modules}		

\section{Code Coverage Metrics}

\bibliographystyle{plainnat}
\bibliography{../../refs/References}

\newpage{}
\section*{Appendix --- Reflection}

The information in this section will be used to evaluate the team members on the
graduate attribute of Reflection.

\input{../Reflection.tex}

\begin{enumerate}
  \item What went well while writing this deliverable?
  \begin{itemize}
    \item Ethan:
    \item Hussain: In this deliverable, we were finally able to get useful, 
    concrete feedback from other people. This was the first time we had a 
    chance to officially show our work to people outside of our team, and it 
    was very helpful. Although we are also stakeholders in this project, showing
    other people that are not as close to the project allowed us to get a 
    different perspective on our work, pointing out things that we had overlooked.
    From this feedback, I look forward to improving our project and making it 
    more user-friendly.
    \item Jeffrey: In this deliverable, we were able to get a lot of feedback and
    put them to action. As a team, we were able to finally get a feel for what
    our users want and how they interact with our product. This was a very important
    step for us, as it was one of the first times we were able to get concrete feedback
    from users which helped guide our development. Additionally, we were able to create
    tests which will be very helpful for us in the future, as it will allow us to catch bugs and
    ensure that our code is working as expected. Overall, I think this was a very productive
    deliverable.
    \item Chengze: One thing that went well during this deliverable was being able to
    see how new users interacted with Flow. Watching people use the system for the
    first time helped us understand which parts of the interface were intuitive and
    which parts were confusing. It was helpful to get feedback from people outside
    the team because they noticed things that we had overlooked. Overall, this
    testing gave us a better idea of how users actually experience our product and
    what we should improve going forward.
    \item Kevin:
  \end{itemize}

  \item What pain points did you experience during this deliverable, and how
    did you resolve them?
  \begin{itemize}
    \item Ethan:
    \item Hussain: One pain point that I experienced during this deliverable was
    the fact that we did not fully consider the unit testing description, when
    planning on completing the deliverable. Though we successfully made the
    unit tests for different parts of our project, we did not have a clear plan
    on how we will categorize them and how we will present them in the report. 
    This caused a bit more last-minute planning and organization, which was
    a bit stressful. 
    \item Jeffrey: One of the biggest pain points I experienced during this deliverable
    was when we were creating tests for our software. I personally create numerous tests for
    specific features I implemented; however, was not aware of how we were supposed to document
    these for the VnV report. This caused a lot of last-minute work to figure out how to categorize and present
    our tests in the report. In the future, I will make sure to have a clear plan for how to document
    tests in the report, so that I can avoid this kind of last-minute stress.
    \item Chengze: One challenge I had during this deliverable was figuring out how to
    present the user testing results clearly in the report. We collected a lot of
    feedback and timing data, but it took some time to decide what information was
    most important to include. To solve this, I focused on linking the testing
    results back to the functional requirements and organizing them in a clearer
    structure. This helped make the evaluation section easier to understand and
    showed how the tests relate to the requirements.
    \item Kevin:
  \end{itemize}
  \item Which parts of this document stemmed from speaking to your client(s) or
  a proxy (e.g. your peers)? Which ones were not, and why?
  \item In what ways was the Verification and Validation (VnV) Plan different
  from the activities that were actually conducted for VnV?  If there were
  differences, what changes required the modification in the plan?  Why did
  these changes occur?  Would you be able to anticipate these changes in future
  projects?  If there weren't any differences, how was your team able to clearly
  predict a feasible amount of effort and the right tasks needed to build the
  evidence that demonstrates the required quality?  (It is expected that most
  teams will have had to deviate from their original VnV Plan.)
\end{enumerate}

\end{document}
